Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-06-28 analy_eval.tex
[draft] anal, def. num changed.

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. If there is no regulator, however, a dilation transformation can rescale both to $1$ and get rid of their dependence. Therefore, regulators are necessary in keeping track of the scale dependence, and physically sensible when considering the lattice realization of the systems.

@@

The Loschmidt echo can be evaluated in the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, it becomes the cylinder partition function between the two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law surge of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.

>>>>

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. Regulators are necessary in keeping track of the scale dependence, otherwise a dilation transformation can rescale both $L$ and $\tau$ to $1$ and get rid of their dependence. The introduction of regulators is also physically sensible when considering the lattice realization of the systems.

@@

The Loschmidt echo can be evaluated in the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulators and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, the diagram becomes the cylinder partition function between the two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can not use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, direct application of the free energy given in App.~\ref{app:lambda_12} will result in a power law surge of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to come from the Schwartzian and outer circle regulator.

### 2017-06-28 def_fidel_echo.tex
[draft] wording changes for descritive text.
[draft] anal, def. num changed.

In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams. It will then be evident that these quantities are just the free energy of boson with conformal interfaces (or boundaries).

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z.
\end{equation}

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as insertion of primary field which is the (bcc) operator. These diagrams then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

>>>>

In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams. We will see that these quantities are just the free energy of boson with conformal interfaces (or boundaries).

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} \equiv |\langle \psi_1 |\psi_2  \rangle |^2 .
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chains (of equal length, hence ``bipartite") and $|\psi_2\rangle$ is that of the connected chains with conformal interface. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represent the disconnected boundary conditions, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z.
\end{equation}

@@

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, the singularities will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay with respect to these scales in the long wavelength limit. In fact, the computations have been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Ward identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L, \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau .
\end{equation}

The tip of the slit is no longer a twist field with the presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and Fig.~\ref{fig:echo} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary CFT point of view, the change of boundary condition can be regarded as inserting a primary field which is a bcc operator. The diagrams for fidelity and echo then become the one point or two point functions of the bcc operators respectively, and the free energy logarithmic term extracts their scaling dimensions.

### 2017-06-28 num_result.tex
[draft] anal, def. num changed.

We finally consider the case
\begin{equation}
\text{P}+\text{P}\rightarrow\lambda+\text{P},
\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_DNDN}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are shifted quadratic curves symmetric about $ \theta = \frac{\pi}{4}$, in accordance to Eq.~\eqref{eq:periodic-case}.

>>>>

We finally consider the case
\begin{equation}
\text{P}+\text{P}\rightarrow\lambda+\text{P},
\end{equation}
in Fig.~\ref{fig:PPPP}. Since ${\rm P} = S_1( \frac{\pi}{4} ) $, the zero mode now occurs at $\theta = \frac{\pi}{4}$. We therefore apply the shift regulator there 
\begin{equation}
\begin{aligned}
\label{eq:approx_DNDN}
S_2\left(\frac{\pi}{4}\right)+S_2\left(\frac{\pi}{4}+\delta\theta\right)\rightarrow S_2(\theta)+S_2\left(\frac{\pi}{4}+\delta\theta\right),
\end{aligned}
\end{equation}
where we take $\delta\theta=0.003\pi$. The $\theta$ dependent exponents now are symmetric about $\theta=\frac{\pi}{4}$ and quadratic on each side, in accordance to Eq.~\eqref{eq:periodic-case}.
